\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-14 ms.tex
mackey

% TODO: after submission?
% - Split cluster into 2? Price-Whelan 1a and 1b?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?
% - With the PM model, go back and apply it to all stars, not just the blue cut. Gets to Sergey / others request to search for evolved stars
% - Is the cluster elongated along its orbit?
% - Describe the strength of the hierarchical cluster params methodology
% - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.

@@

The mass and age of \clustername\ are comparable to Milky Way disk open clusters, but with a much lower metallicity, and a much larger spatial extent.
For example, the Pleiades has an age $\sim 135~\textrm{Myr}$ \citep{Gossage:2018}, but a physical size $\sim 5~\textrm{pc}$.
At a distance of $\cldist$, \clustername\ spans $\sim 1.5^\circ$, corresponding to a physical size $\sim 700$--$800~\textrm{pc}$.
If it formed unbound, but with an initial size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.
\todo{Compare the size with systems in http://adsabs.harvard.edu/abs/2017MNRAS.472.2975M - (see eg their fig 4, 6)}

@@

\section{Conclusions} \label{sec:conclusion}

>>>>

% TODO: after submission?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?
% - With the PM model, go back and apply it to all stars, not just the blue cut. Gets to Sergey / others request to search for evolved stars
% - Is the cluster elongated along its orbit?
% - Describe the strength of the hierarchical cluster params methodology
% - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.

@@

The mass and age of \clustername\ are comparable to Milky Way disk open clusters, but with a much lower metallicity, and a much larger spatial extent.
For example, the Pleiades has an age $\sim 135~\textrm{Myr}$ \citep{Gossage:2018}, but a physical size $\sim 5~\textrm{pc}$.
At a distance of $\cldist$, \clustername\ spans $\sim 1.5^\circ$, corresponding to a physical size $\sim 700$--$800~\textrm{pc}$.
This is more comparable to (but still larger than) recent star formation sites in the Magellanic bridge \citep[e.g.,][]{Mackey:2017}, which likely formed as a result of the violent interaction between the MCs.
If \clustername\ formed unbound, but with an initial size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.

@@

\section{Summary} \label{sec:conclusion}
